### 2018-11-14 Sections/quantum_genetic_medicine.tex
Finished indexing hierarchy
Quantum ecosystems
ryser

\section{Quantum genetic medicine}\index{Genetics!Medicine}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{genetic_sequencing_de_novo}
	\captionspacefig \caption{Three short-reads, each of 10 base-pairs in length (blue), which we wish to assemble into the largest possible contig\index{Contigs} belonging to the underlying genome. The specificity\index{Specificity} defines the number of endpoint base-pairs that must overlap for them to be considered a match (orange). In this case the specificity is 3, and 3 short-reads have been assembled into a single 24 base-pair contig. The greater the specificity the more accurate will be the matching, but the lower the probability of finding matches. A specificity too low will create false matches, whereas a specificity too high makes finding sufficiently overlapping short-reads unlikely. This makes optimum choice of specificity an important consideration, creating a direct tradeoff between reconstructed contig length and accuracy. This sequencing technique is best applied when there is no known reference genome for the data under analysis. For the technique to work effectively there must be a sufficient quantity of short-read data that with high probability overlaps between reads will exist. If the data is too sparse few overlaps are likely to be found. Thus, average reconstructed contig lengths grow with the amount of short-read data available to the engine.} \label{fig:gen_seq_de_novo}
\end{figure}

@@

The other approach, \textit{mapping}, is to use an existing genome as a reference\index{Reference genome}. Rather than piece short-reads together, we compare them against this reference to infer their relative locations in the genome. When doing so, we allow some error threshold\index{Error threshold} in the matching. Specifically, we require the Hamming distance\index{Hamming distance} between a short-read and an equally-long segment of the reference be below some threshold. The flexibility offered by this threshold accommodates for mutational differences between the reference and the short-reads\index{Genetics!Mutations} (i.e the SNPs), which is ultimately what we wish to characterise.

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{genetic_sequencing_mapping}
	\captionspacefig \caption{In genome mapping we begin with a known reference genome (blue) to act as a comparison for short-reads (orange). The short-reads are slid along the reference until a location with sufficient overlap is found, at which point we record a match. By allowing some degree of single nucleotide mismatches (green) between the reference and short-read, we are able to characterise the SNPs in the short-read data. This sequencing technique is appropriate when we have a known genome for the species to which the short-read data belongs, but we wish to identify minor genetic mutations between the samples. For example, mapping short-reads belonging to human cancer cells to a human reference genome characterises the genetic mutations associated with that particular cancer. The technique works with any amount of short-read data, even just a single read, provided the reference is known.} \label{fig:gen_seq_mapping}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{genetic_medicine_pipeline}
	\captionspacefig \caption{Pipeline for quantum-enhanced genetic drug development. A quantum search algorithm searches over algorithmically-generated drug compounds or functional groups, for each performing Hamiltonian simulation, to determine if its score is above a threshold. The quantum search subroutine yields a quadratic enhancement in the number of drugs that can be simulated in parallel, and the Hamiltonian simulation subroutine yields an exponential enhancement over classical simulation techniques.} \label{fig:genetic_med_pipe}
\end{figure}

>>>>

\section{Quantum genetic medicine}\index{Genetics!Medicine}\label{sec:genetic_medicine}

@@

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{genetic_sequencing_de_novo}
\else
	\includegraphics[clip=true, width=0.7\textwidth]{genetic_sequencing_de_novo}
\fi
	\captionspacefig \caption{Three short-reads, each of 10 base-pairs in length (blue), which we wish to assemble into the largest possible contig\index{Contigs} belonging to the underlying genome. The specificity\index{Specificity} defines the number of endpoint base-pairs that must overlap for them to be considered a match (orange). In this case the specificity is 3, and 3 short-reads have been assembled into a single 24 base-pair contig. The greater the specificity the more accurate will be the matching, but the lower the probability of finding matches. A specificity too low will create false matches, whereas a specificity too high makes finding sufficiently overlapping short-reads unlikely. This makes optimum choice of specificity an important consideration, creating a direct tradeoff between reconstructed contig length and accuracy. This sequencing technique is best applied when there is no known reference genome for the data under analysis. For the technique to work effectively there must be a sufficient quantity of short-read data that with high probability overlaps between reads will exist. If the data is too sparse few overlaps are likely to be found. Thus, average reconstructed contig lengths grow with the amount of short-read data available to the engine.} \label{fig:gen_seq_de_novo}
\end{figure}

@@

The other approach, \textit{mapping}, is to use an existing genome as a reference\index{Genome!Reference}. Rather than piece short-reads together, we compare them against this reference to infer their relative locations in the genome. When doing so, we allow some error threshold\index{Error threshold} in the matching. Specifically, we require the Hamming distance\index{Hamming distance} between a short-read and an equally-long segment of the reference be below some threshold. The flexibility offered by this threshold accommodates for mutational differences between the reference and the short-reads\index{Genetics!Mutations} (i.e the SNPs), which is ultimately what we wish to characterise.

@@

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{genetic_sequencing_mapping}
\else
	\includegraphics[clip=true, width=0.7\textwidth]{genetic_sequencing_mapping}
\fi
	\captionspacefig \caption{In genome mapping we begin with a known reference genome (blue) to act as a comparison for short-reads (orange). The short-reads are slid along the reference until a location with sufficient overlap is found, at which point we record a match. By allowing some degree of single nucleotide mismatches (green) between the reference and short-read, we are able to characterise the SNPs in the short-read data. This sequencing technique is appropriate when we have a known genome for the species to which the short-read data belongs, but we wish to identify minor genetic mutations between the samples. For example, mapping short-reads belonging to human cancer cells to a human reference genome characterises the genetic mutations associated with that particular cancer. The technique works with any amount of short-read data, even just a single read, provided the reference is known.} \label{fig:gen_seq_mapping}
\end{figure}

@@

\begin{figure}[!htbp]
\if 2\pubmode
\includegraphics[clip=true, width=0.475\textwidth]{genetic_medicine_pipeline}
\else
\includegraphics[clip=true, width=0.7\textwidth]{genetic_medicine_pipeline}
\fi
	\captionspacefig \caption{Pipeline for quantum-enhanced genetic drug development. A quantum search algorithm searches over algorithmically-generated drug compounds or functional groups, for each performing Hamiltonian simulation, to determine if its score is above a threshold. The quantum search subroutine yields a quadratic enhancement in the number of drugs that can be simulated in parallel, and the Hamiltonian simulation subroutine yields an exponential enhancement over classical simulation techniques.} \label{fig:genetic_med_pipe}
\end{figure}
